---
title: "Week 07 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Exercises

```{r}
if(! require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse,
  here
)

getwd()

source("/Users/alexismerritt/Documents/FoundationsR/week_07/hw_functions.R")
```

1.  Describe some of the benefits of using functions.

##Functions are useful tools when you need to run the same process over a series of values in a list or if it is a process that you need for a variety of different projects. You can set up the function so that it may be called by any number of project without needing to rewrite it over and over again

2.  Practice turning the following code snippets into functions. Think about what each function does. What would you call it? How many arguments does it need? Can you rewrite it to be more expressive or less duplicative?

```{r}
mean(is.na(x))

x / sum(x, na.rm = TRUE)

sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE)
```

```{r}
#this first function calculates the average number of missing values in a set

Average_Missing_Values <- function(value){
  Sum_Val <- sum(value)
  
  if (is.na(value) == TRUE) {
    missing <- missing + 1 }
  else {
    return("not missing")
  }
  
  return(missing/Sum_Val)
  
}
 
##This function returns a list of the ratio each value in the list to the sum of the list

Sum_Ratio <- function(value2){
  
  if (is.na(value2) == True ) {
    return(NA)
  }else {
    
    Sum_val <- sum(value2)
    
    return(value2/Sum_val)
    
  }
}

 #This function calculates the coefficient of variation

Coef_Var <- function(value3) {
  
  if (is.na(value3) == TRUE) {
    return(NA)
  }else {
    std = sd(value3)
    avg = mean(value3)
    
    return(std/avg)
  }
  
  
}
  
```


3.  Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```{r}
f1 <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}
f2 <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}
f3 <- function(x, y) {
  rep(y, length.out = length(x))
}
```



4.  Implement a fizzbuzz function. It takes a single number as input. If the number is divisible by three, it returns "fizz". If it's divisible by five it returns "buzz". If it's divisible by three and five, it returns "fizzbuzz". Otherwise, it returns the number. Make sure you first write working code before you create the function.

```{r}
fizzbuzz <- function(x) {
  
  for (i in x) {
    if (i%%3 == 0 && i %%5 == 0 ) {
      output[i] <- "FizzBuzz"
    } else if (i %% 3 == 0) {
      output[i] <- "Fizz"
    } else if (i %% 5 == 0) {
      output[i] <- "Buzz"
    }
    
  }
  
  
}
```


We'll be working with national baby names data from the [Social Security Administration](https://www.ssa.gov/oact/babynames/limits.html)

5. The following code will create your data frame:

```{r US names}
files <- list.files("/Users/alexismerritt/Documents/FoundationsR/week_07/Data", pattern = "\\.txt", full.names = T)

names_df <- map_df(files, ~read_name(.))
```

```{r}
names_df
```

Describe what the `read_name` function is doing.

6.  Create a function that allows a user to select a name (or names) and graph its trend over time.

* If multiple names are selected, they should each be represented on the graph as a unique color.
* The user should be able to select whether they want to graph based upon the `count` or the `rank` of the name.
* The user should be able to indicate if they are interested in male names, female names, or either.

```{r}
baby_names <- function(df,Name, base, sex, na.rm = TRUE) {
  
  df %>% 
    ggplot(aes(x = year,
               y = base,)) +
    geom_bar(aes(fill = sex,
                 color = Name))
  
  
}
```


7. Create a repository for your course project and share it with @rharrington31. Your project should include:

* A `README.md` file
* A script (whether it is a script or a markdown file) that successfully ingests your data for your analysis.
